Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-27 leadership_across_cultures_contexts.Rmd
Code to output pvclust to pdf. Insert pngs into doc.

```{r groupsex, fig.width=15, fig.cap="The distribution of text records by group type and leader sex. Areas of the bars are proportional to the number of text records in that category. There were no female leaders in any military or religious group."}
plot_group_sex
```

@@

```{r qualcluster, fig.cap="Cluster analysis of leader quality variables. Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
plot(m_pvclust_qual)
pvrect(m_pvclust_qual, alpha = 0.9)
```

```{r funcluster, fig.cap="Cluster analysis of leader function variables. Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
plot(m_pvclust_fun)
pvrect(m_pvclust_fun, alpha = 0.9)
```

>>>>

```{r groupsex, fig.width=15, fig.height=15, fig.cap="The distribution of text records by group type and leader sex. Areas of the bars are proportional to the number of text records in that category. There were no female leaders in any military or religious group."}
plot_group_sex
```

@@

```{r qualcluster, fig.cap="Cluster analysis of leader quality variables. Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
# plot(m_pvclust_qual)
# pvrect(m_pvclust_qual, alpha = 0.9)
knitr::include_graphics("Figures/m_pvclust_qual.final.png")
```

```{r funcluster, fig.cap="Cluster analysis of leader function variables. Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
# plot(m_pvclust_fun)
# pvrect(m_pvclust_fun, alpha = 0.9)
knitr::include_graphics("Figures/m_pvclust_fun.final.png")
```
